---
title: "README"
author: "baptiste"
date: "8/6/2017"
output: 
  md_document:
    variant: markdown_strict+autolink_bare_uris
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = ".")
```

## The problem with LaTeX templates

Practically every journal supplying a TeX template defines its own custom macros for author affiliations and other metadata, with very little consistency from one publisher to another. This renders the process of re-submitting a manuscript to a new journal really cumbersome. Consider the following two examples:

**OSA**
```{tex OSA, eval=FALSE}
\title{Manuscript Title}

\author[1,2,3]{Author One}
\author[2,*]{Author Two}

\affil[1]{First address}
\affil[2]{Second address}
\affil[3]{Third address}

\affil[*]{Corresponding author: email@my-email.com}
\dates{Compiled \today}
\ociscodes{(140.3490) Lasers, distributed feedback; (060.2420) Fibers.}
```

**ACS**
```{tex ACS, eval=FALSE}
\title{Manuscript title}

\author{Author One}
\affiliation{First address}
\alsoaffiliation{Second address}
\email{email@my-email.com}

\author{Author Two} 
\phone{+123456789}
\fax{+123456789}
\email{email@my-email.com}
\affiliation{First address}
\alsoaffiliation{Second address}
\alsoaffiliation{Third address}

\abbreviations{IR,NMR,UV}
\keywords{American Chemical Society}
```

## A standardised, human-readable format

We'll store the metadata in an external file, in `yaml` format.

```
title: On physics and chemistry

authors:
  - name: Lise Meitner
    affiliation: [Kaiser Wilhelm Institute,
                University of Berlin,
                Manne Siegbahn Institute]
    email: lise.meitner@institution.edu

  - name: Pierre Curie
    affiliation: École Normale Supérieure
    email: pierre.curie@institution.edu
    homepage: https://en.wikipedia.org/wiki/Pierre_Curie
    
  - name: Marie Curie
    affiliation: [University of Paris,
                 Institut du Radium,
                 École Normale Supérieure]
    email: marie.curie@institution.edu
    homepage: https://en.wikipedia.org/wiki/Marie_Curie
    phone: +123456
    fax: 123456

collaboration: Wikipedia
thanks: Friends and colleagues
keywords: [physics, science, everything]
abbreviations: [UV,IR]
pacs: [123, 456, 789] # https://publishing.aip.org/publishing/pacs
ociscodes: [123, 456, 789] # https://www.osapublishing.org/submit/ocis
preprint: APS/123-ABC
```

This file can contain more information than needed, and is common to all versions of the manuscript, regardless of the publisher's template. From these data, we will populate the TeX macros relevant to a given TeX template as needed.

Below's a partial example to illustrate the process.

```{r test, warning=FALSE,  message=FALSE}
library(yaml)
library(glue)

meta <- yaml.load_file("_metadata.yaml")


fun_title <- function(meta) glue_data(meta, "\\title{{ {title} }}") 
fun_authors <- function(meta) lapply(meta[["authors"]], 
                                     glue_data, 
                                     '\\author{{ {name} }}
                                     { paste(sprintf("\\\\affiliation{%s}", affiliation), collapse="\\n") }')

preamble_journal <- list(title = fun_title, authors = fun_authors)
lapply(preamble_journal, do.call, list(meta=meta))
```

## TODO list

- compile a list of TeX templates
- turn them into glue templates
- fine-tune the glueing process (line breaks, strange characters, etc.)
- wrap into a package (cf Rticles)
- make a Rstudio add-in


